### 2023-03-08 manuscript.tex
Fixing the size of Mastodon's icon [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f2068e319930774a03f19646dc6c571d617a9f34.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f2068e319930774a03f19646dc6c571d617a9f34/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366818427

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d}{SORTEE-Github-Hackathon/manuscript@c6a8b5b}
on March 8, 2023.

@@

  · \includegraphics{images/mastodon.svg}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f2068e319930774a03f19646dc6c571d617a9f34/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f2068e319930774a03f19646dc6c571d617a9f34}{SORTEE-Github-Hackathon/manuscript@f2068e3}
on March 8, 2023.

@@

  · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
